The Social Conditioning of Fear

### 2023-12-06 scripts/manuscript.qmd
contextual factors lit

Individuals' report of fear have been shown to relate to a wide range of contextual factors, such as neighborhood composition and community crime rates [@hale1996; @warr1990], and individual sociodemographic characteristics, such as gender, sexual orientation, income, age, health condition, and immigration status [@lagrange1989; @otis2007; @madriz2023].

Especially, the role of gender in fear of crime has been well documented in victimization research [@stanko1993; @snedker2006; @schnitzer2010].

>>>>

Individuals' report of fear have been shown to relate to a wide range of contextual factors, such as neighborhood composition and community crime rates [@hale1996; @warr1990], and individual sociodemographic characteristics, such as gender, sexual orientation, income, age, health condition, and immigration status [@lagrange1989; @otis2007; @madriz2023]. To be more specific, this body of scholarship has found spatial and neighborhood characteristics have a significant impact on individuals' self-reported fear of crime, as those who live in areas with high levels of community disorder have reported more fear than those who do not live in such communities [@rountree1996]. Also, due to the popularity density in urban areas, residents of these areas have reported higher levels of fear at night, potentially because of feelings of alienation and unfamiliarity among residents [@bennett1994].

Especially, the role of gender in fear of crime has been well documented in victimization research [@cops2011; @snedker2006; @schnitzer2010].

[@stanko1993]
